\documentclass{article}

\title{User Guide}
\author{Andrew Ye and Diva Shah}
\date{May 2024}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage
\section{Object}
The object of the game is to become the last player standing and earn the most protons, which is the currency. 
\section{Preparation}
Place the board on a table and put the Question Cards face down on the designated space on the board (Labeled “Place Question Cards Here”). Then, each player must roll a dice to choose a token to represent themselves while traveling around the board and decide who begins the game. The highest roller will begin the game and gets to choose their token first. This is important as the atomic number of the element that each token represents is the least number of protons that the player must have at all times. If the player goes under this limit and cannot reach it by passing GO, they lose the game. The four options for the tokens are a Banana, representing Potassium, a Shell, representing Calcium, an Egg, representing Sulfur, and a Lightbulb, representing Argon. Therefore, the player with the Banana token loses the game whenever they have less than 19 protons and cannot reach this limit by passing GO. The limits for each token are listed below:\\ 
Banana: Potassium- 14 protons minimum (by passing GO, you can reach the total of 19 protons)\\
Shell: Calcium- 15 protons minimum (by passing GO, you can reach the total of 20 protons) \\
Egg: Sulfur- 11 protons minimum (by passing GO, you can reach the total of 16 protons) \\
Lightbulb: Argon- 13 protons minimum (by passing GO, you can reach the total of 19 protons) \\
Each player must be given 60 protons (represented by the red beads) to start. The rest of the protons will go to the bank. 
\section{Banker}
Select as Banker a player who will also make a good Auctioneer. A Banker who plays in the game must keep their personal funds separate from those of the Bank. When more than five persons play, the Banker may elect to act only as Baner and Auctioneer.
\section{The Bank}
Besides the Bank’s protons, the Bank holds the Deed cards prior to purchase and use by the players. The Bank sells auctions properties and hands out their proper Title Deed cards. The Bank collects all taxes, fines, loans and interest, and the price of all properties which it sells and auctions. The Bank can never run out of money, the Banker may increase the money in circulation by introducing protons into the economy.
\section{The Play}
Starting with the Banker, each player in turn throws the dice. The player with the highest total starts the play: Place your token on the corner marked “GO,” throw the dice and move your token in the direction of the arrow the number of spaces indicated by the dice. After you have completed your play, the turn passes to the left. The tokens remain on the spaces occupied and proceed from that point on the player’s next turn. Two or more tokens may rest on the same space at the same time.\\ 
According to the space your token reaches, you may be entitled to buy properties – or obligated to pay rent, pay taxes, Go to Jail, or draw a question card.\\ 
	If you throw doubles, you move your token as usual, the sum of the two dice, and are subject to any privileges or penalties pertaining to the space on which you land. Retaining the dice, throw again and move your token as before. If you throw doubles three times in succession, move your token immediately to the space marked “in Jail.”
“GO”: Each time a player’s token lands on or passes over GO, the Banker pays them a 5 proton salary or the player can choose to take a question card without the prospect of losing protons. 

\section{Buying Property}
Whenever you land on an unowned property you may buy that property from the Bank at its printed price. You receive the Title Deed card showing ownership; place it face up before you.\\ 
	If you do not wish to buy the property, the Banker sells it at auction to the highest bidder. The buyer pays the Bank the amount of the bid in protons and receives the Title Deed card for that property. Any player may bid. Bidding may start at any price.

\section{Paying Rent}
When you land on property owned by another player, the owner collects rent from you in accordance with the list printed on its Title Deed card. 

\section{Question Spaces}
When you land on the “Question” space, take the top card from the deck of question cards. Based on the Question number listed on the card, address the Question bank provided and have the player to your left ask you the question(answers are listed at the back). Follow the directions on the card depending on if you got the question correct or incorrect. 

\section{Income Tax}
If you land on the tax space, pay the tax as directed on the space. 

\section{Jail}
You land in Jail when (1) your token lands on the space marked “Go to Jail” (2) you throw doubles three times in succession. When you are sent to Jail, you cannot collect your 5 proton salary in that move regardless of where your token is on the board. Your turn ends when you are sent to Jail. 

\section{Stability}
A player landing on this place does not receive any money, property, or reward. This is a free “resting space”. 

\section{Bankruptcy/Loss}
You are declared bankrupt, or lose when the amount of protons that you have is less than the minimum amount required by your token. For example, the minimum amount required for each token is: 
Banana- 19\\
Shell- 20\\
Lightbulb-18\\
Egg- 16\\
If you cannot reach this amount by passing go in the current round, you lose the game and must return your properties and protons back to the bank. (i.e. Banana must always have at least 14 protons, Shell must always have at least 15 protons, Lightbulb must always have at least 13 protons, and Egg must always have 11 protons.)

\section{Miscellaneous}
Protons may not be loaned to another player by either the bank or another player. 



\end{document}
